%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Surya Dheeshjith} % Your name
%\address{156 Kasturi, Balajinagar, Sangli 416416} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
 % Your phone number and email
\address{+91-8971711811 \\ surya.dheeshjith@gmail.com }
\address{GitHub : \url{https://github.com/SuryaDhee}}
\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Career Objective}
To work for an organization which provides me the opportunity to improve my skills and knowledge to grow along with the organization objective.
\end{rSection}
\begin{rSection}{Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills \ & Machine Learning, Click Fraud Detection, Android App Development \\
Development Languages \ & C, C++, Python, Java, MySQL, HTML, CSS  \\
Software \& Tools & \ Xcode, Scikit-Learn, Numpy, Pandas, Anaconda3, Android Studio, \\ \ & Eclipse, Latex, Kali Linux, MATLAB \& Simulink
\end{tabular} 
\end{rSection}
\begin{rSection}{Education}

{\bf R.V. College of Engineering} \hfill {\em August 2017 - Present} 
\\ Bachelor of Engineering\hfill {\em CGPA : 9.53}  \\
Computer Science and Engineering\\
{\bf Sri Kumarans Children's Home, Bangalore} \hfill {\em June 2016 - May 2017} 
\\ 12th Standard (Senior Secondary Examination)\hfill { Percentage: 93.2 }
\\CBSE\\
{\bf Sri Kumarans Children's Home, Bangalore} \hfill {\em June 2014 - May 2015} 
\\ 10th Standard (Secondary Examination)\hfill { CGPA : 9.6 }
\\CBSE
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}


%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Certification}
Graph Theory - NPTEL [2019] \hfill {  Percentage : 81\% }\\
Computer Architecture - NPTEL [2018] \hfill { Percentage : 92\% }\\
Discrete Mathematics - NPTEL [2018] \hfill { Percentage : 94\% }\\
Programming, Data Structures and Algorithms using Python - NPTEL [2018] \hfill { Percentage : 84\% }\\
\end{rSection}

\begin{rSection}{Online Courses \& Workshops}
HTML,CSS,JAVASCRIPT - Udemy [2018] \\
Machine Learning in Python - Udemy [2018] \\
Self Driving Fundamentals (Apollo) - Udacity [2018] \\
Cloud Fundamentals and Machine Learning on Azure - Microsoft Workshop [2019]\\
IoT based transport system for smart mobility - CISCO Workshop[2019]\\


\end{rSection}
\begin{rSection}{Work Experience}
\begin{rSubsection}{Discovery Lab, SCIS, FIU}{Miami, FL}{Research Intern}{\em June 2019 - July 2019}
Conducted research in the field of Machine Learning for a period of two months under the guidance of Thejas G. S. and Dr. S.S. Iyengar. The research involved developing a supervised learning model to detect click fraud in online advertisements. 
\end{rSubsection}

\end{rSection}

\begin{rSection}{Projects}
{\bf CFXGB: An Optimized \& Effective Learning Approach for Click Fraud Detection }
\\CFXGB is a machine learning model that detects click fraud in online advertisements. \\
{\bf College Announcements Application}\\
This project is an application developed on Android Studio using Java. The app contains different announcements from college and is updated in realtime using Firebase Cloud Service \\
{\bf Elevator with Hand Recognition}\\
This project shows the movement of an elevator based on the user's gestures. The users show their choice outside the elevator by holding out fingers to indicate the floor number they wish to go to.\\
{\bf File System with Shell}\\
This project implements a file system through a command line shell. The files are stored on a user defined virtual disk. Different commands can be executed in the shell to create, open, list and clear the files.
\end{rSection}

\begin{rSection}{Presentations \& talks}
SCIS, FIU, Miami, Florida : Paper proposal and presentation of research to Dr. S.S. Iyengar and other esteemed faculty.
\end{rSection}

\begin{rSection}{Publications}
Thejas G.S., {\bf Surya Dheeshjith}, Dr. S.S. Iyengar, Dr. N.R. Sunitha, Prajwal Badrinath. CFXGB:
An Optimized \& Effective Learning Approach for Click Fraud Detection. In ACM Transactions on Autonomous and Adaptive Systems, 2019. (Under Review)
\end{rSection}

\begin{rSection}{Achievements \& Awards} 
Top 5\% of certified candidates in Graph Theory course, Nptel, 2019\\
Nominated and Selected for research intern at Florida International University, Miami, FL, USA, 2019.
Top 5\% of certified candidates in Discrete Mathematics course, Nptel, 2018\\
Top 1\% of certified candidates in Computer Architecture course, Nptel, 2018\\
Nominated for Best Self Study in Data Structures in C, 2018.\\
Awarded Most Logical Thinker in Senior Secondary, 2017.\\
Distinction in Mathematics in Education Assessment Australia, 2014.\\

\end{rSection}

\begin{rSection}{References} 
\item Dr. S.S. Iyengar, Distinguished University Professor, Director and Ryder Professor, School of Computing and Information Sciences, Florida International University. \\Email : iyengar@cis.fiu.edu; Contact : +1 305-348-3947.
\item Dr. N.R. Sunitha, Professor, Dept. of Computer Science \& Engineering, Siddaganga Institute of Technology.
\\Email : nrsunitha@gmail.com; Contact : +91 9986276851.
\item Prof. Thejas G.S., Graduate Research Assistant, Discovery 
Lab, FIU MOU Program Activity Coordinator, Florida International University and Asst. Prof, Dept. of CSE, Siddaganga Institute of Technology.\\ Email : tgs001@fiu.edu; Contact : +1 786-451-4841
\item Dr. Shobha G., Professor, Dept. of Computer Science \& Engineering, R.V. College of Engineering.\\
Email : shobhag@rvce.edu.in; Contact : +91 9480280273
\end{rSection}

\end{document}
